\subsection{Domain analysis}
The term $g_{outsider}$ introduced in \ref{regmodqual} may be extended to
cover multiple comparisons: a $g$ may be classified as an ``outsider'' by
multiple models simultaniously. We propose a term $g_{outsider}^{multiple}$ to
denote such $g$, and $g_{outsider}^{once}$ denote a special case when a $g$ was
classified as ``outsider'' only by one model. We aregue that
$g_{outsider}^{multiple}$ are stronger candidates for an HGT event, or an event
of a detected contamination of a number of genome assembiles. To gain a better
understanding of the nature of the $g_{outsider}^{multiple}$s we chose to
analyse their putative domain structure.

We used PFAM-A \cite{Finn2014} database and HMMER \cite{Prakash2017} to search
for known domains in all PPSs with 3 or more hits in other genomes. 
For each genome, we compared the number of genes with each discovered PFAM domain
between the core and both $g_{outsider}^{once}$ and $g_{outsider}^{multiple}$ sequences.
We used a chi-square test to assess whether any domains were significantly
over- or underrepresented among outsider multiple sequences.  We considered
p-values of 5.86E-07=0.005/85254 to be statistically significant (a Bonferroni
correction for multiple comparisons was applied to account for 85252
domain/species combinations used in the analysis). Note that technically this
is not a strict statistical procedure, since similar genes will have similar
arrays of bit scores and our classification of these genes will not be
independent. Similarly, this does not distinguish multiple HGT events of
sequences containing the same PFAM domain from a single HGT event followed by
multiple gene duplications. Main findings were evaluated manually.
