\subsection{Outsider detection}
We performed 61*60/2 = 1830 in silico metagenomic experiments involving a total
of 296639 predicted protein-coding sequences, each of which had a hit in at
least 3 other genomes. A total of 67\% of the obtained regression models were successfully validated and thus allowed the distinction between the sequences of two genomes.
Let us use the Drosophila simulans/Wolbachia in silico metagenomic experiment as an example of what was done.
Figure 1 shows a principal component analysis (PCA) visualization of sequence clustering based on the normalized values of similarity scores for the Drosophila simulans and Wolbachia metagenomic experiment. A clear separation of sequences can be observed even without the use of regression analysis by PCA alone; however, we used PCA analysis only for illustrative purposes.
The majority of sequences (288012, 97.1\%) from each analyzed genome were
classified as core sequences in all metagenomic experiment with validated
regression models. 4279 (1.4\%) of the sequences were classified as “outsider
once”. The remaining 4348 (1.5\%) sequences were classified as “outsider
multiple” and are the most likely candidates for HGT. The list of
protein-coding open reading frames classified as “outsider once”, or “outsider
multiple” along with their FASTA sequences is available for download: link.The
fraction of “outsider once” and “outsider multiple” genes varies from genome to
genome, as shown on Figure 4.An important limitation is that our approach does not distinguish HGT from genomic contaminations. Thus the observed differences in Core/Outsider ratio between different genomes, does not necessarily indicate that some genomes are more prone to the acquisition of sequences due to HGT.
We used a PFAM analysis to check for any PFAM domains are significantly
overrepresented in “outsider multiple” sets of sequences. A list of top-ranked
findings (ranked by significance) is presented in Table 1.We would like to
highlight some of the most interesting findings.
